### 2019-10-01 uiuc.tex
Grammatical edits suggested by smpark7, Roberto, and Jack

\subsubsection{Accessibility and Accomodation}
 Many hotels are located around downtown Champaign and the Eastern 
 side of campus, making transportation easy. Champaign-Urbana Mass Transit 
 (CU-MTD) is a reliable public transportation service that sees millions of 
 riders every year. CU-MTD charges an affordable rate of \$1 per ride, which 
 can be paid in cash or using the Token Transit app. Additionally, an all-day 
 pass can be bought on Saturdays and Sundays for \$2 from any bus operator or 
 from the app. All CU-MTD busses are wheelchair accessible. Rental bikes and 
 rideshare services are also plentiful.
 Champaign's Willard Airport (CMI) is just 15 minutes from campus and has 
regular flights to and from Chicago O’Hare (ORD), Dallas/Fort Worth (DFW), and 
Charlotte (CLT).  Other nearby airports include Chicago (ORD and MDW),
Indianapolis (IND), and Bloomington (BMI). If attendees fly into these
airports, ground transportation to the Champaign area will be required. To this
end, Peoria Charter is a popular bus service with several 
daily trips between the UIUC campus and the Chicagoland area.

\subsubsection{Weather}
With an average high temperature of 65$^{\circ}$ and an average low temperature 
of 40$^{\circ}$, April in Champaign is a gorgeous month of dwindling winter 
weather and spring coming into bloom. Holding a conference during this time 
will be the perfect way to showcase our beautiful city.

\subsection{University of Illinois at Urbana-Champaign: Learning \& Labor}
\begin{wrapfigure}{r}{0.5\textwidth}
  \begin{center}
  \vspace{-\baselineskip}
    \includegraphics[width=0.44\textwidth]{alma.jpg}
    \caption{Alma Mater accompanied by Learning and Labor}
  \end{center}
\end{wrapfigure}
Founded in 1867, the University of Illinois at Urbana-Champaign (UIUC) has cultivated a long history of significant scientific discoveries and contributions. The theory of superconductivity, the invention of the transistor, the discovery of archaea, the fourth domain of life, and the first web browser are just some of the many breakthroughs that came out of UIUC. The famous Morrow Plots, established in 1876, became the first research crop field at a university and is still used today. Attendees might also be familiar with Blue Waters, one of the world’s fastest supercomputers. 
The UIUC Grainger College of Engineering has had sixteen Nobel Laureates in physics. Including John Bardeen, the only scientist to ever win the award in physics twice. It also offers 15 different majors to almost 6000 undergraduate and 2500 graduate students. Of its twelve ranked majors, nine are ranked among the top 10 in the nation, and six of which remain ranked among the top 5 in their degree. Overall, the Grainger College of Engineering in Urbana-Champaign ranks sixth among the nation’s best undergraduate engineering programs. With more than 250 degrees for undergraduates and graduates and a multitude of first-class research facilities and resource, UIUC gives its nearly 45,000 students the ability to succeed.

@@

The ANS-UIUC maintains and develops a cohesive community of students in nuclear engineering. It also engages in education and outreach programs to teach members of the surrounding community about nuclear science. One of our most popular outreach programs is Engineering Open House (EOH), during which ANS-UIUC repeatedly earns awards for best presentation of a society. EOH is an annual event where members of the local community, from young children to senior adults, visit the engineering campus to learn more about STEM research. Membership is currently around 70-80 students and has been steadily growing. The chapter works to host events catering to nuclear, plasma, and radiological concentrations. Professional development plays a crucial role in student development, and it is the biggest part of member involvement at UIUC. Professional development activities range from tours of various facilities to pizza with campus visitors. Some of the past tours have included Clinton Power Station, Curium Pharma through UIUC Women In Nuclear, Oak Ridge National Laboratory, Analysis System (ANSYS) Inc, and Argonne National Laboratory. ANS-UIUC has historically been one of the best represented institutions at the annual student conference and is a tradition this chapter is eager to uphold.

@@

\begin{figure}[H]
  \centering
  \begin{subfigure}{0.5\textwidth}
    \centering
    \includegraphics[width=8cm]{ans_uiuc_group.jpg}
    \subcaption{ANS Barbeque 2019}
  \end{subfigure}%
  \begin{subfigure}{0.5\textwidth}
    \centering
    \includegraphics[width=8cm]{ans_conf_19.jpg}
    \subcaption{ANS Student Conference 2019 at VCU}
  \end{subfigure}   
\end{figure}

@@

\subsection{Research at UIUC}
Faculty and students in the Department of Nuclear, Plasma, and Radiological Engineering (NPRE) at Illinois conduct research in many areas of interest to the nuclear science community. Both graduate and undergraduate  students actively participate and make their own atomic contributions that will someday save the world.
Research programs in Nuclear, Plasma, and Radiological Engineering at the University of Illinois at Urbana-Champaign can be
broadly classified into five areas:
\begin{itemize}
        \item \textbf{Nuclear Power} (reactor physics, thermalhydraulics, fuel cycle, radiation transport, I\&C)
        \item \textbf{Plasma and Fusion} (modeling, plasma-material interactions)
        \item \textbf{Radiological Sciences} (detectors, imaging, health physics, medical applications)
        \item \textbf{Material Science} (nuclear fuels, structural materials)
        \item \textbf{Risk and Policy} (PRA, safety, energy, arms controls, disarmament, security)
\end{itemize}

@@

\subsubsection{Nuclear Power}
NPRE is well known for its pioneering research in the area of reactor power engineering. Graduates have gone on to leadership positions in industry, national laboratories, and academia. Research in the Nuclear Power concentration covers all aspects of power generation using nuclear energy on land, underwater (submarine), and in space. It is inherently interdisciplinary and relies on several branches of physics and engineering for design and analysis of large complex systems. These include aspects of reactor physics, reactor thermal-hydraulics, reactor safety, reliability and risk, instrumentation and control, training and education, human factors engineering, reactor materials, nonproliferation, and more. Safety starndards and maintenance for existing reactors and new reactor designs are also explored by faculty in the department. Crosscutting areas of research include multi-physics and multi-scale modeling and simulation, high performance computing, reliability and risk, validation and verification, and uncertainty analysis. Recently, the University of Illinois declared a plan to be completely carbon-neutral by 2050. Nuclear power is the perfect candidate to help UIUC attain its carbon reduction and energy goals. Together, the University and the NPRE department are saving the world one atom at at time.

\subsubsection{Plasma Physics and Fusion Science}
\begin{wrapfigure}{r}{0.5\textwidth}
  \begin{center}
  \vspace{-\baselineskip}
    \includegraphics[width=0.48\textwidth]{hidra.png}
    \caption{The Hybrid Illinois Device for Research and Application (HIDRA)}
  \end{center}
\end{wrapfigure}
The Fusion and Plasma Physics research theme in the NPRE department has a long history of work in the area of magnetic and inertial nuclear fusion as well as plasma engineering. NPRE is now one of the leading departments in plasma-material interactions with its Center for Plasma-Materials Interactions established by Prof. David Ruzic. Furthermore, in the past few years, three new faculty members have been added to this area including: Prof. Davide Curelli and Prof. Daniel Andruzcyk. There are five research themes that spans the work in fusion and plasma physics: fusion materials, plasma-material interface (PMI) diagnostics, plasma-edge and PMI modeling, plasma nanosynthesis, and plasma sources and processing. The Hybrid Illinois Device for Research and Application (HIDRA) marks the newest addition to the team at CPMI. This device finished construction and achieved first plasma during the spring of 2016. \\

@@

\begin{itemize}
  \item \textbf{Advanced Reactors and Fuel Cycles (ARFC)} - \textit{Dr. Kathryn Huff}\\
  The ARFC group seeks to advance the safety and sustainability of nuclear energy production through improved reactor designs, fuel cycle strategies, and waste management techniques. In the area of advanced reactors, our work focuses on extending current simulation tools with features essential to advanced reactor multiphysics. In the context of the broader nuclear fuel cycle, the ARFC group emphasizes modeling, simulation, and analysis of the global nuclear fuel cycle, with an emphasis on sustainability. A crosscutting theme of our research is an emphasis on advancing methods and software for computational nuclear engineering. Accordingly, the Advanced Reactors and Fuel Cycles group is proud to be affiliated with the University of Illinois National Center for Supercomputing Applications and its Blue Waters computing facility.
  \item \textbf{Virtual Education and Research Laboratory (VERL)} - \textit{Dr. Rizwan Uddin}\\
  The VERL group focuses on the development of innovative numerical methods and their implementation on high performance computing machines. Research efforts center on problems in nuclear engineering, with emphasis on thermal-hydraulics and reactor physics.

  \item \textbf{Analysis of Reactor Transients and Stability (ARTS)} - \textit{Dr. Tomasz Kozlowski}\\
  The ARTS group performs deterministic safety analysis by developing and validating advanced methods to accurately determine reactor safety margins and reactor behavior. By performing high-fidelity numerical predictions of the reactor behavior in abnormal transient scenarios of safety significance, our work supports the nuclear reactor safety analysis, and increases the fidelity of primary system simulation. This approach is at the heart of nuclear power’s excellent safety record – always striving to improve current tools and methods.

@@

  \item \textbf{Non-Equilibrium Matter Laboratory} - \textit{Dr. Yang Zhang}\\
  This laboratory focuses on the study of non-equilibrium matter, with particular emphasis on liquids and soft matter, using integrated neutron and synchrotron light experimental probes and atomistic modeling and simulation. The structure and dynamics of these systems are either inherently complex or driven away from equilibrium by extreme conditions. In particular, our current interests include a range of fundamental and technical problems involving slow phenomena and rare events, such as: materials far from equilibrium and in extreme environments; extreme properties of liquids; and glassy or jammed soft matters.

@@

  \item \textbf{Laboratory: Nuclear Materials Fabrication and Studies Lab} - \textit{Dr. Brent Heuser}\\
  The Radiation Detection and Imaging Lab focuses on developing non-invasive imaging technology for use in preclinical medical research. Many of our current endeavors focus on developing semiconductor Single Photon Emission Computed Tomography (SPECT) and Positron Emission Tomography (PET). These works challenge the current state of the art for spatial resolution and system sensitivity. The use of highly pixelated CdTe detectors has driven our work to break into a spatial resolution on the order of 300 microns for both PET and SPECT. Our work in SPECT has also challenged the limits of aperture sensitivity through the engineering of the compound-eye aperture.

>>>>

\subsubsection{Accessibility and Accomodation}
 A large number of hotels are located around downtown Champaign and the Eastern side of campus, making transportation easy. Champaign-Urbana Mass Transit (CU-MTD) is a reliable public transportation service that sees millions of riders every year. CU-MTD charges an affordable rate of \$1 per ride, which can be paid in cash or using the Token Transit app. Additionally, an all-day pass can be bought on Saturdays and Sundays for \$2 from any bus operator or from the app. All CU-MTD busses are wheelchair accessible. Rental bikes and rideshare services are also plentiful. There is a small airport, Willard Airport, just 20 minutes from campus that has regular flights to and from Chicago O’Hare and Dallas Fort Worth airports. Finally, Peoria Charter is a popular bus service with several daily trips between the UIUC campus and the Chicagoland area.

\subsubsection{Weather}
With an average high temperature of 65$^{\circ}$ and an average low temperature of 40$^{\circ}$, April in Champaign is a gorgeous month of dwindling winter weather and spring coming into bloom. Holding a conference during this time would be the perfect way to showcase our beautiful city.

\subsection{University of Illinois at Urbana-Champaign: Learning \& Labor}
\begin{wrapfigure}{r}{0.5\textwidth}
  \begin{center}
  \vspace{-\baselineskip}
    \includegraphics[width=0.44\textwidth]{alma.jpg}
    \caption{Alma Mater accompanied by Learning and Labor}
  \end{center}
\end{wrapfigure}
Founded in 1867, the University of Illinois at Urbana-Champaign (UIUC) has cultivated a long history of significant scientific discoveries and contributions. The theory of superconductivity, the invention of the transistor, the discovery of archaea, the fourth domain of life, and the first web browser are just some of the many breakthroughs that came out of UIUC. The famous Morrow Plots, established in 1876, became the first research crop field at a university and is still used today. Attendees might also be familiar with Blue Waters, one of the world’s fastest supercomputers. 
The UIUC Grainger College of Engineering has had sixteen Nobel Laureates in physics, including John Bardeen, the only scientist to ever win the award in physics twice. It also offers 15 different majors to almost 6000 undergraduate and 2500 graduate students. Of its twelve ranked majors, nine are ranked among the top 10 in the nation, and six of which remain ranked among the top 5 in their degree. Overall, the Grainger College of Engineering in Urbana-Champaign ranks sixth among the nation’s best undergraduate engineering programs. With more than 250 degrees for undergraduates and graduates and a multitude of first-class research facilities and resource, UIUC gives its nearly 45,000 students the ability to succeed.

@@

The ANS-UIUC maintains and develops a cohesive community of students in nuclear engineering. It also engages in education and outreach programs to teach members of the surrounding community about nuclear science. One of our most popular outreach programs is Engineering Open House (EOH), an annual event where members of the local community, from young children to senior adults, visit the engineering campus to learn more about STEM research; ANS-UIUC has repeatedly earned awards for best presentation of a society at EOH. Membership is currently around 70-80 students and has been steadily growing. The chapter works to host events catering to nuclear, plasma, and radiological concentrations. Professional development plays a crucial role in student development, and it is the biggest part of member involvement at UIUC. Professional development activities range from tours of various facilities to pizza with campus visitors. Some of the past tours have included Clinton Power Station, Curium Pharma through UIUC Women In Nuclear, Oak Ridge National Laboratory, Analysis System (ANSYS) Inc, and Argonne National Laboratory. ANS-UIUC has historically been one of the best represented institutions at the annual student conference and is a tradition this chapter is eager to uphold.

@@

\begin{figure}[H]
  \centering
  \begin{subfigure}{0.5\textwidth}
    \centering
    \includegraphics[width=8cm]{ans_uiuc_group.jpg}
    \subcaption{ANS Barbeque 2019}
  \end{subfigure}%
  \begin{subfigure}{0.5\textwidth}
    \centering
    \includegraphics[width=8cm]{ans_conf_19.jpg}
    \subcaption{ANS Student Conference 2019 at VCU}
  \end{subfigure}   
  \caption{ANS Activities}
\end{figure}

@@

\subsection{Research at UIUC}
Faculty and students in the Department of Nuclear, Plasma, and Radiological Engineering (NPRE) at Illinois conduct research in many areas of interest to the nuclear science community. Both graduate and undergraduate  students actively participate and make their own atomic contributions that will someday save the world.
Research programs in Nuclear, Plasma, and Radiological Engineering at the University of Illinois at Urbana-Champaign can be
broadly classified into five areas:
\begin{itemize}
        \item \textbf{Nuclear Power} (reactor physics, thermal hydraulics, fuel cycle, radiation transport, I\&C)
        \item \textbf{Plasma and Fusion} (modeling, plasma-material interactions)
        \item \textbf{Radiological Sciences} (detectors, imaging, health physics, medical applications)
        \item \textbf{Material Science} (nuclear fuels, structural materials)
        \item \textbf{Risk and Policy} (PRA, safety, energy, arms controls, disarmament, security)
\end{itemize}

@@

\subsubsection{Nuclear Power}
NPRE is well known for its pioneering research in the area of reactor power engineering. Graduates have gone on to leadership positions in industry, national laboratories, and academia. Research in the Nuclear Power concentration covers all aspects of power generation using nuclear energy on land, underwater (submarine), and in space. It is inherently interdisciplinary and relies on several branches of physics and engineering for design and analysis of large complex systems. These include aspects of reactor physics, reactor thermal-hydraulics, reactor safety, reliability and risk, instrumentation and control, training and education, human factors engineering, reactor materials, nonproliferation, and more. Safety standards and maintenance for existing reactors and new reactor designs are also explored by faculty in the department. Crosscutting areas of research include multi-physics and multi-scale modeling and simulation, high performance computing, reliability and risk, validation and verification, and uncertainty analysis. Recently, the University of Illinois declared a plan to be completely carbon-neutral by 2050. Nuclear power is the perfect candidate to help UIUC attain its carbon reduction and energy goals. Together, the University and the NPRE department are saving the world one atom at at time.

\subsubsection{Plasma Physics and Fusion Science}
\begin{wrapfigure}{r}{0.5\textwidth}
  \begin{center}
  \vspace{-\baselineskip}
    \includegraphics[width=0.48\textwidth]{hidra.png}
    \caption{The Hybrid Illinois Device for Research and Application (HIDRA)}
  \end{center}
\end{wrapfigure}
The Fusion and Plasma Physics research concentration in the NPRE department has a long history of work in the area of magnetic and inertial nuclear fusion as well as plasma engineering. NPRE is now one of the leading departments in plasma-material interactions with its Center for Plasma-Materials Interactions established by Prof. David Ruzic. Furthermore, in the past few years, two new faculty members have been added to this area: Prof. Davide Curelli and Prof. Daniel Andruzcyk. There are five research themes that spans the work in fusion and plasma physics: fusion materials, plasma-material interface (PMI) diagnostics, plasma-edge and PMI modeling, plasma nanosynthesis, and plasma sources and processing. The Hybrid Illinois Device for Research and Application (HIDRA) marks the newest addition to the team at CPMI. This device finished construction and achieved first plasma during the spring of 2016. \\

@@

\begin{itemize}
  \item \textbf{Advanced Reactors and Fuel Cycles (ARFC)} - \textit{Dr. Kathryn Huff}\\
  The ARFC group seeks to advance the safety and sustainability of nuclear energy production through improved reactor designs, fuel cycle strategies, and waste management techniques. In the area of advanced reactors, their work focuses on extending current simulation tools with features essential to advanced reactor multiphysics. In the context of the broader nuclear fuel cycle, the ARFC group emphasizes modeling, simulation, and analysis of the global nuclear fuel cycle, with an emphasis on sustainability. A crosscutting theme of our research is an emphasis on advancing methods and software for computational nuclear engineering. Accordingly, the Advanced Reactors and Fuel Cycles group is proud to be affiliated with the University of Illinois National Center for Supercomputing Applications and its Blue Waters computing facility.
  \item \textbf{Virtual Education and Research Laboratory (VERL)} - \textit{Dr. Rizwan Uddin}\\
  The VERL group focuses on the development of innovative numerical methods and their implementation on high performance computing machines. Research efforts center on problems in nuclear engineering, with emphasis on thermal-hydraulics and reactor physics.

  \item \textbf{Analysis of Reactor Transients and Stability (ARTS)} - \textit{Dr. Tomasz Kozlowski}\\
  The ARTS group performs deterministic safety analysis by developing and validating advanced methods to accurately determine reactor safety margins and reactor behavior. By performing high-fidelity numerical predictions of the reactor behavior in abnormal transient scenarios of safety significance, their work supports the nuclear reactor safety analysis, and increases the fidelity of primary system simulation. This approach is at the heart of nuclear power’s excellent safety record – always striving to improve current tools and methods.

@@

  \item \textbf{Non-Equilibrium Matter Laboratory} - \textit{Dr. Yang Zhang}\\
  This laboratory focuses on the study of non-equilibrium matter, with particular emphasis on liquids and soft matter, using integrated neutron and synchrotron light experimental probes and atomistic modeling and simulation. The structure and dynamics of these systems are either inherently complex or driven away from equilibrium by extreme conditions. In particular, their current interests include a range of fundamental and technical problems involving slow phenomena and rare events, such as: materials far from equilibrium and in extreme environments; extreme properties of liquids; and glassy or jammed soft matters.

@@

  \item \textbf{Laboratory: Nuclear Materials Fabrication and Studies Lab} - \textit{Dr. Brent Heuser}\\
  The Radiation Detection and Imaging Lab focuses on developing non-invasive imaging technology for use in preclinical medical research. Many of their current endeavors focus on developing semiconductor Single Photon Emission Computed Tomography (SPECT) and Positron Emission Tomography (PET). These works challenge the current state of the art for spatial resolution and system sensitivity. The use of highly pixelated CdTe detectors has driven their work to break into a spatial resolution on the order of 300 microns for both PET and SPECT. Their work in SPECT has also challenged the limits of aperture sensitivity through the engineering of the compound-eye aperture.
